Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-05-26 paper-amia-2018/manuscript.tex
update manuscript

Although punctuation mark plays an important role in segmentation boundary detection and large numbers of errors were encountered by the false positive of boundary identification. For example, a text block ``A1 A2 A3. B1 B2 B3. C1 C2 C3 C4.'' can be incorrectly segmented at position A3, B3 and C4 where a punctuation mark was encountered. Similarly, additional information is the common reason for the classified original segment into multiple segments. For instance, the above text block can also be incorrectly segmented at position B3 and C4 if the third sentence (C) only provides a supportive information of MI code associated with first two sentences (A and B).

>>>>

Although punctuation mark plays an important role in segmentation boundary detection and large numbers of errors were encountered by the false positive of boundary identification. For example, a text segment from an e-Coaching email \textit{``A typical day in regards to fruit and vegetable has me eating about a serving at breakfast (our caf has cut up fruit) and then maybe a piece of fruit later in the day or as a snack. Vegetable tends to be a side serving at lunch and dinner and I get celery or carrot cuts with dressing for a snack a lot of times. I could probably add some sort of vegetable into my breakfast (like spinach in an omelet) and snack on another piece of fruit when I quotemark m hungry rather than the junk food I tend to eat.''} incorrectly segmented after the first sentence where a punctuation mark was encountered. Similarly, additional information is a common cause for misclassification of an email segment into multiple segments. For instance, the first sentence of the above email segment represents a positive commitment to adolescent's behavior change then next two sentences provide an additional information to support their commitment.
